\textbf{How to measure maximally precise radial velocities from a set of spectra:\\ The time-independent spectrum case}

### 2021-06-12 paper/eprv.tex
Updates from Overleaf

% To-do items
% -----------
% - search for all \todo
% - search for all HOGG
% - search for all BEDELL
% - search for all CITE
% - should we fun-cite some ancient papers in the first paragraph, like Hubble and Oort?

@@

\keywords{\raggedright
atmospheric~effects
---
binaries:~spectroscopic
---
methods:~data analysis
---
methods:~statistical
---
techniques:~radial~velocities
---
planets~and~satellites:~detection
}

>>>>

% To-do items
% -----------
% - update aastex and keywords
% - search for all \todo
% - search for all HOGG
% - search for all BEDELL
% - search for all CITE
% - should we fun-cite some ancient papers in the first paragraph, like Hubble and Oort?

@@

\keywords{\raggedright
\todo{there is a new keyword set; these are wrong now:}
atmospheric~effects
---
binaries:~spectroscopic
---
methods:~data analysis
---
methods:~statistical
---
techniques:~radial~velocities
---
planets~and~satellites:~detection
}
